---
title: "Individual_Project_1"
author: "Gabriel Leornas BSIT-2A"
date: "2022-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages that will be needed 

```{r, run}
library("twitteR") 
library(dplyr)
library(tidyr)
library("plotly")
library(ggplot2)
library(RColorBrewer)
library(tidytext)
library(rtweet)
library(tm)
library(slam)
library(wordcloud)
library(wordcloud2)
library(corpus)
```


##1. Extract from twitter using your developer's credentials. Choose any keyword you want. 



#Set-up credentials

```{r, credentials}
CONSUMER_SECRET <-"2vmVGAlukrEnyO9f20nEtJfv96GEFBFbe7e8CuwFGl9ozY9kSi"
CONSUMER_KEY <-"l5CSikp1YC2oBdmLh08DDMDoc"
ACCESS_SECRET <- "dNFeJKTMdBixOaJBn6YXBsOCaybvBWBw8YxvnuTBgeApu" 
ACCESS_TOKEN <- "1596107281610858498-FjtGw5XzODkRVyfEGvjQX5xo8bPIF4" 


```



#connect to twitter app

```{r, commect}
setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```



##2. Get 10000 observations "excluding retweets.



#Getting a data
#it would take few minutes to load which depend the number of data you need

#but when you already save this data as a file you can skip this part.

```{r, num2}
trendTweets <- searchTwitter("#Anime -filter:retweets",
                             n = 10000,
                             lang = "en",
                             since = "2022-11-20",
                             until = "2022-11-30",
                             retryOnRateLimit = 120)

trendTweets
save(trendTweetsDF,file = "trendingTweetsDF.Rdata")

```

```{r, head}
head(trendTweets)
```



#Converting data into dataframe
```{r, conver}
trendTweetsDF <- twListToDF(trendTweets)
class(trendTweetsDF)
names(trendTweetsDF)
View(trendTweetsDF)
head(trendTweetsDF)[1:5]
head(trendTweetsDF$text)[1:5]

```

#Saving the data into a file

```{r, trendT}
save(trendTweetsDF,file = "trendingTweetsDF.Rdata")
load(file = "trendingTweetsDF.Rdata")
```



#Checking for missing values in a data frame

```{r, check}
sapply(trendTweetsDF, function(x) sum(is.na(x)))
```

#Subsetting using the dplyr()package

```{r, subset}
tweetsDF <- trendTweetsDF %>%
  select(screenName,text,created,statusSource)
```

#saving file as Rdata

```{r, save}
save(tweetsDF, file = "tweetsDF.Rdata")
load(file = "tweetsDf.Rdata")
```



##3. Plot the time series from the date created. with legends.



#plotting time series graph using plot() by rtweet package base on the date created.

```{r, oneseven}
ggplot(data = tweetsDF, aes(x = created), fill = tweetsDF) +
  geom_histogram(aes(fill = ..count..)) + 
  theme(legend.position="right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "aquamarine4", high = "midnightblue")
```


##4. Plot a graph (any graph you want)  based on the type of device - found in Source
#- that the user use. Include the legends.



```{r, graph}
encodeSource <- function(x) {
  if(grepl(">Twitter for iPhone</a>", x)){
    "iphone"
  }else if(grepl(">Twitter for iPad</a>", x)){
    "ipad"
  }else if(grepl(">Twitter for Android</a>", x)){
    "android"
  } else if(grepl(">Twitter Web Client</a>", x)){
    "Web"
  } else if(grepl(">Twitter for Windows Phone</a>", x)){
    "windows phone"
  }else if(grepl(">dlvr.it</a>", x)){
    "dlvr.it"
  }else if(grepl(">IFTTT</a>", x)){
    "ifttt"
  }else if(grepl(">Facebook</a>", x)){
    "facebook"
  }else {
    "others"
  }
}


tweetsDF$tweetSource = sapply(tweetsDF$statusSource, 
                              encodeSource)

tweet_appSource <- tweetsDF %>% 
  select(tweetSource) %>%
  group_by(tweetSource) %>%
  summarize(count=n()) %>%
  arrange(desc(count)) 

Source_subset <- subset(tweet_appSource,count >10)
```



```{r, df}
dataDF <- data.frame(
  category = tweet_appSource$tweetSource,
  count = tweet_appSource$count
)

dataDF$fraction = dataDF$count / sum(dataDF$count)
dataDF$percentage = dataDF$count / sum(dataDF$count) * 100
dataDF$ymax = cumsum(dataDF$fraction)
dataDF$ymin = c(0, head(dataDF$ymax, n=-1))
dataDF$roundP = round(dataDF$percentage, digits = 2)
```



#plotting using geom_bar() - bar graph

```{r, graph2}
ggplot(tweetsDF[tweetsDF$tweetSource != 'others',], aes(tweetSource, fill = tweetSource)) +
  geom_bar() +
  theme(legend.position="right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Number of tweets") +
  ggtitle("Tweets by Source")
```



##5. Create a wordcloud from the screenName



#Using wordcloud() package but using a shape pentagon 

```{r, cloud}
tweet_appScreen <- tweetsDF %>%
  select(screenName) %>%
  group_by(screenName) %>%
  summarize(count=n()) %>%
  arrange(desc(count)) 

```

#convert to Corpus

```{r, convert}
namesCorpus <- Corpus(VectorSource(tweetsDF$screenName))  #using ScreenName
class(tweetsDF$screenName)

```

#Running the code using the wordcloud()

```{r, wordcloudTWO}
wordcloud2(data=tweet_appScreen, 
           size=0.8, 
           color='random-light',
           shape = 'pentagon')

```
